
### Individual model, data load and process
```{r}
data_join = read_csv('./data/author_project_join_com_Python_year_before_2015.csv')


data_join_no_outlier = subset(data_join, technical_contain > 0
                                       & social_strength < exp(3)& woc_within_one_hop_count > exp(0.5))


hist(log(data_join$woc_within_one_hop_count+1))

hist(data_join$technical_contain)
hist(log(data_join$social_strength+1))

hist(data_join$technical_contain_percentile)
hist(data_join$social_strength_percentile)


```

### Individual model, logistic regression model
```{r}


model_individual = glmer(join_flag~
      + log(social_strength + 1)
      + technical_contain
      + (1|author)
      , data = data_join_no_outlier
      , nAGQ = 0
      ,control=glmerControl(optimizer = "nloptwrap")
      ,family = "binomial")

vif(model_individual)
summary(model_individual)
anova(model_individual)
r.squaredGLMM(model_individual)



model_individual_competition = glmer(join_flag~
      + log(social_strength + 1)
      + technical_contain
      + log(woc_within_one_hop_count + 1)
      + social_strength_percentile
      + technical_contain_percentile
      + (1|author)
      , data = data_join_no_outlier
      ,nAGQ = 0
      ,control=glmerControl(optimizer = "nloptwrap")
      ,family = "binomial")
vif(model_individual_competition)
summary(model_individual_competition)
anova(model_individual_competition)
r.squaredGLMM(model_individual_competition)

```

### Individual model, generate Table 3
```{r}
stargazer(model_individual, model_individual_competition, omit = c('Constant'), digits = 2, omit.stat = c('ser', 'll', 'aic', 'bic'), single.row = TRUE, star.cutoffs = c(.05, .01, .001), star.char = c("*", "**", "***"), covariate.labels = c('Social strength (log)', 'Technical similarity', 'Number of competing projects (log)','Social strength percentile', 'Technical similarity percentile'))


```

### Project model, data load and process
```{r}
library(car)
library(lme4)
library(MuMIn)
library(relaimpo)

year_string = '2018'

data_survival = read_csv(sprintf('./data/regre_survival_analysis_com_Python_survival_year_before_2022_period_year_at_%s.csv', year_string))
sum(data_survival$new_attracted_author_count_one_year_all)
sum(data_survival$new_attracted_author_count_one_year_has_embedding)

data_basic_network = read_csv(sprintf('./data/regre_basic_network_metrics_com_Python_survival_year_before_2022_period_year_at_%s.csv', year_string))


data_chara = read_csv(sprintf('./data/regre_individual_chara_com_Python_survival_year_before_2022_period_year_at_%s.csv', year_string))

data_merge = merge(data_survival, data_basic_network,by = 'woc')

data_merge = merge(data_merge, data_chara,by = 'woc')
length(unique(data_merge$woc))


hist(log(data_merge$project_age+1))
hist(log(data_merge$used_by_woc+1))
hist(log(data_merge$imported_by_woc+1))
hist(log(data_merge$all_dev_alltime_count+1))
hist(log(data_merge$all_dev_recent_count+1))
hist(log(data_merge$all_past_commit_count+1))
hist(log(data_merge$recent_past_commit_count+1))
hist(log(data_merge$all_has_embedding_social_within_one_hop_count+1))

hist(log(data_merge$new_attracted_author_count_one_year_all+1))
hist(log(data_merge$new_attracted_author_count_one_year_has_embedding+1))

hist(log(data_merge$individual_value_agg+1))
hist(log(data_merge$all_value_agg+1))

if (year_string == '2015'){
data_merge_no_outlier = subset(data_merge,   project_age > exp(2) & project_age < exp(9)
                                           & used_by_woc < exp(6)
                                           & imported_by_woc < exp(6)
                                           & all_dev_alltime_count < exp(6)
                                           & all_dev_recent_count < exp(4)
                                           & all_past_commit_count < exp(10)
                                           & recent_past_commit_count < exp(8)
                                           & new_attracted_author_count_one_year_all < exp(4)
                                           & new_attracted_author_count_one_year_has_embedding < exp(3)
                                           & individual_value_agg < exp(3)
                                           & all_value_agg < exp(2)
                                      )
}else if(year_string == '2016'){
   data_merge_no_outlier = subset(data_merge,   project_age > exp(2) & project_age < exp(9)
                                           & used_by_woc < exp(6)
                                           & imported_by_woc < exp(6)
                                           & all_dev_alltime_count < exp(6)
                                           & all_dev_recent_count < exp(4)
                                           & all_past_commit_count < exp(10)
                                           & recent_past_commit_count < exp(10)
                                           & all_has_embedding_social_within_one_hop_count < exp(9)
                                           & new_attracted_author_count_one_year_all < exp(4)
                                           & new_attracted_author_count_one_year_has_embedding < exp(3)
                                           & individual_value_agg < exp(3)
                                           & all_value_agg < exp(2)
                                      )
}else if(year_string == '2017'){
   data_merge_no_outlier = subset(data_merge,   project_age > exp(1) & project_age < exp(9)
                                           & used_by_woc < exp(6)
                                           & imported_by_woc < exp(6)
                                           & all_dev_alltime_count < exp(6)
                                           & all_dev_recent_count < exp(4)
                                           & all_past_commit_count < exp(10)
                                           & all_past_commit_count > exp(2)
                                           & recent_past_commit_count < exp(10)
                                           & all_has_embedding_social_within_one_hop_count < exp(9)
                                           & new_attracted_author_count_one_year_all < exp(4)
                                           & new_attracted_author_count_one_year_has_embedding < exp(3)
                                           & individual_value_agg < exp(3)
                                           & all_value_agg < exp(1)
                                      )
}else if(year_string == '2018'){
   data_merge_no_outlier = subset(data_merge,   project_age > exp(2) & project_age < exp(8.5)
                                           & used_by_woc < exp(6)
                                           & imported_by_woc < exp(4)
                                           & all_dev_alltime_count < exp(6)
                                           & all_dev_recent_count < exp(4)
                                           & all_past_commit_count < exp(10)
                                           & all_past_commit_count > exp(2)
                                           & recent_past_commit_count < exp(8)
                                           & all_has_embedding_social_within_one_hop_count < exp(10)
                                           & new_attracted_author_count_one_year_all < exp(4)
                                           & new_attracted_author_count_one_year_has_embedding < exp(3)
                                           & individual_value_agg < exp(3)
                                           & all_value_agg < exp(2)
                                      )
}

```

### Project model, regression
```{r}
regression_no_environment = lm(log(new_attracted_author_count_one_year_has_embedding + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                          ,data = data_merge_no_outlier)
vif(regression_no_environment)
summary(regression_no_environment)
anova(regression_no_environment)



regression_basic = lm(log(new_attracted_author_count_one_year_has_embedding + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                          ,data = data_merge_no_outlier)

vif(regression_basic)
summary(regression_basic)
anova(regression_basic)


regression_individual = lm(log(new_attracted_author_count_one_year_has_embedding + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                              + log(individual_value_agg + 1)
                                          ,data = data_merge_no_outlier)

vif(regression_individual)
summary(regression_individual)
anova(regression_individual)


regression_full = lm(log(new_attracted_author_count_one_year_has_embedding + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                              + log(all_value_agg+1)
                                          ,data = data_merge_no_outlier)



bootresults = boot.relimp(regression_full, b = 100)
ci<-booteval.relimp(bootresults)
plot(ci)
ci$est['log(all_has_embedding_social_within_one_hop_count + 1).lmg']
ci$est['log(all_value_agg + 1).lmg']

vif(regression_full)
summary(regression_full)
Anova(regression_full)

```

### Project model, generate Table 4, and Table 6-8 in the supplementary material
```{r}
library(stargazer)
stargazer(regression_no_environment, regression_basic, regression_individual, regression_full, omit = c('Constant'), digits = 2, omit.stat = c('ser', 'f', 'rsq'), single.row = TRUE, star.cutoffs = c(.05, .01, .001), star.char = c("*", "**", "***"),
          covariate.labels = c('Project age (log)', 'Project total developer size (log)', 'Project recent developer size (log)', 'Project total commits (log)', 'Project recent commits (log)', 'Project code reuse (log)', 'Project dependency (log)', 'Has readme', 'Has license', 'Labor pool size (log)','Effective size, no-competing variables (log)', 'Effective size, full variables (log)'))


```

### Project model, validation; negative bionminal regression
```{r}


regression_no_environment_nb = glm.nb(new_attracted_author_count_one_year_has_embedding~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                          ,data = data_merge_no_outlier)

regression_basic_nb = glm.nb(new_attracted_author_count_one_year_has_embedding~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                              ,data = data_merge_no_outlier)


regression_individual_nb = glm.nb(new_attracted_author_count_one_year_has_embedding~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                              + log(individual_value_agg+1)
                                              ,data = data_merge_no_outlier)

regression_full_nb = glm.nb(new_attracted_author_count_one_year_has_embedding~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                              + log(all_value_agg+1)
                                          ,data = data_merge_no_outlier)


summary(regression_no_environment_nb)
summary(regression_basic_nb)
summary(regression_individual_nb)
summary(regression_full_nb)


```
### Project model, generate Table 9 in the supplementary material
```{r}

library(stargazer)
stargazer(regression_no_environment_nb, regression_basic_nb, regression_individual_nb, regression_full_nb, omit = c('Constant'), digits = 2, omit.stat = c('ser', 'f', 'rsq'), single.row = TRUE, star.cutoffs = c(.05, .01, .001), star.char = c("*", "**", "***"),
          covariate.labels = c('Project age (log)', 'Project total developer size (log)', 'Project recent developer size (log)', 'Project total commits (log)', 'Project recent commits (log)', 'Project code reuse (log)', 'Project dependency (log)', 'Has readme', 'Has license', 'Labor pool size (log)','Effective size, no-competing variables (log)', 'Effective size, full variables (log)'))


```

### Project model, validation; outcome variable being all new contributors
```{r}


regression_no_environment_allnew = lm(log(new_attracted_author_count_one_year_all + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                          ,data = data_merge_no_outlier)
vif(regression_no_environment_allnew)
summary(regression_no_environment_allnew)
anova(regression_no_environment_allnew)



regression_basic_allnew = lm(log(new_attracted_author_count_one_year_all + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                          ,data = data_merge_no_outlier)

vif(regression_basic_allnew)
summary(regression_basic_allnew)
anova(regression_basic_allnew)


regression_individual_allnew = lm(log(new_attracted_author_count_one_year_all + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                              + log(individual_value_agg + 1)
                                           
                                          ,data = data_merge_no_outlier)

vif(regression_individual_allnew)
summary(regression_individual_allnew)
anova(regression_individual_allnew)


regression_full_allnew = lm(log(new_attracted_author_count_one_year_all + 1)~
                                                log(project_age + 1)
                                              + log(all_dev_alltime_count + 1)
                                              + log(all_dev_recent_count + 1)
                                              + log(all_past_commit_count + 1)
                                              + log(recent_past_commit_count + 1)
                                              + log(used_by_woc + 1)
                                              + log(imported_by_woc + 1)
                                              + as.logical(woc_has_readme_flag)
                                              + as.logical(woc_has_license_flag)
                                              + log(all_has_embedding_social_within_one_hop_count + 1)
                                              + log(all_value_agg+1)
                                          ,data = data_merge_no_outlier)



bootresults = boot.relimp(regression_full_allnew, b = 100)
ci<-booteval.relimp(bootresults)
plot(ci)
ci$est['log(all_has_embedding_social_within_one_hop_count + 1).lmg']
ci$est['log(all_value_agg + 1).lmg']


```
### Project model, generate Table 5 in the supplementary material
```{r}
library(stargazer)
stargazer(regression_no_environment_allnew, regression_basic_allnew, regression_individual_allnew, regression_full_allnew, omit = c('Constant'), digits = 2, omit.stat = c('ser', 'f', 'rsq'), single.row = TRUE, star.cutoffs = c(.05, .01, .001), star.char = c("*", "**", "***"),
          covariate.labels = c('Project age (log)', 'Project total developer size (log)', 'Project recent developer size (log)', 'Project total commits (log)', 'Project recent commits (log)', 'Project code reuse (log)', 'Project dependency (log)', 'Has readme', 'Has license', 'Labor pool size (log)','Effective size, no-competing variables (log)', 'Effective size, full variables (log)'))


```


### Generate Figure 3
```{r}

df_visu = data.frame()
year_string_list = c('2015', '2016', '2017', '2018')
for (year_string in year_string_list)
{
print(year_string)
data_validation = read_csv(sprintf('./data/validation_new_developer_com_Python_year_at_%s.csv', year_string))

data_validation$has_embedding_new_developer_count = data_validation$one_hop_new_author_has_embedding_count + data_validation$two_hop_new_author_has_embedding_count + data_validation$three_hop_new_author_has_embedding_count + data_validation$fourormore_hop_new_author_has_embedding_count


has_embedding_new_dev_ratio = sum(data_validation$has_embedding_new_developer_count) / sum(data_validation$total_new_author_count)
one_hop_has_embedding_new_dev_ratio = sum(data_validation$one_hop_new_author_has_embedding_count) / sum(data_validation$has_embedding_new_developer_count)
two_hop_has_embedding_new_dev_ratio = sum(data_validation$two_hop_new_author_has_embedding_count) / sum(data_validation$has_embedding_new_developer_count)
three_hop_has_embedding_new_dev_ratio = sum(data_validation$three_hop_new_author_has_embedding_count) / sum(data_validation$has_embedding_new_developer_count)

no_colab_all_new_dev_ratio = sum(data_validation$no_collab_new_author_all_count) / sum(data_validation$total_new_author_count)


one_hop_all_new_dev_ratio = sum(data_validation$one_hop_new_author_all_count) / sum(data_validation$total_new_author_count)
two_hop_all_new_dev_ratio = sum(data_validation$two_hop_new_author_all_count) / sum(data_validation$total_new_author_count)
three_hop_all_new_dev_ratio = sum(data_validation$three_hop_new_author_all_count) / sum(data_validation$total_new_author_count)

df_embedding = data.frame(matrix(ncol = 6, nrow = 1))
colnames(df_embedding) <- c('one_hop', 'two_hop', 'three_hop', 'four_or_more_hop', 'year', 'type')
df_embedding$one_hop = one_hop_has_embedding_new_dev_ratio
df_embedding$two_hop = two_hop_has_embedding_new_dev_ratio
df_embedding$three_hop = three_hop_has_embedding_new_dev_ratio
df_embedding$four_or_more_hop = 1 - one_hop_has_embedding_new_dev_ratio - two_hop_has_embedding_new_dev_ratio - three_hop_has_embedding_new_dev_ratio
df_embedding$year = as.integer(year_string)
df_embedding$type = 'embedding'
df_visu = rbind(df_visu, df_embedding)


df_all = data.frame(matrix(ncol = 6, nrow = 1))
colnames(df_all) <- c('one_hop', 'two_hop', 'three_hop', 'four_or_more_hop', 'year', 'type')
df_all$one_hop = one_hop_all_new_dev_ratio
df_all$two_hop = two_hop_all_new_dev_ratio
df_all$three_hop = three_hop_all_new_dev_ratio
df_all$four_or_more_hop = 1 - one_hop_all_new_dev_ratio - two_hop_all_new_dev_ratio - three_hop_all_new_dev_ratio
df_all$year = as.integer(year_string)
df_all$type = 'all'
df_visu = rbind(df_visu, df_all)

}



df_visu_long = pivot_longer(df_visu, cols = 'one_hop':'four_or_more_hop', names_to ='distance', values_to = 'ratio')
df_visu_long[df_visu_long$distance == 'one_hop',]$distance <- 'one hop'
df_visu_long[df_visu_long$distance == 'two_hop',]$distance <- 'two hop'
df_visu_long[df_visu_long$distance == 'three_hop',]$distance <- 'three hop'
df_visu_long[df_visu_long$distance == 'four_or_more_hop',]$distance <- 'four or more hop'

df_visu_long$distance = as.factor(df_visu_long$distance)
df_visu_long <- df_visu_long %>%
  mutate( distance=factor(distance,levels=c("one hop", "two hop", "three hop", "four or more hop")) )
df_visu_long$year = as.factor(df_visu_long$year + 1)
df_visu_long_embedding = subset(df_visu_long, type == 'embedding')
df_visu_long_all = subset(df_visu_long, type == 'all')

p2 = ggplot(df_visu_long_embedding, aes(fill=year, y=ratio, x=distance)) + 
    geom_bar(position="dodge", stat="identity", width = 0.75)+
scale_fill_manual('year', values = c('2016' = "blue",'2017' = "yellow", '2018' = "orange", '2019' = 'red'))+
  ggtitle("New contributors with at least ten past commits")+
  xlab('Shortest network distance from existing developers')+
   ylab("Ratio of new developers")+
theme(plot.title = element_text(hjust = 0.5,size = 22),
        legend.text = element_text(size=20),
        axis.text=element_text(size=20),
        axis.title=element_text(size=20),
      legend.title=element_text(size=22))+
   ylim(0,1)
p2
ggsave(file="./figure/new_contributors.pdf", width=12, height=9, dpi=300)

```
